Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 Background/history.tex
final touches to www paper

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered reported Common Vulnerabilities and Exposures
(CVE)~\cite{cve} to get an idea of the distribution of
reported \ehi over time. We found 28 reports, shown in
Table~\ref*{tab:history}. It can be seen that even though many vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.

>>>>

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered reported Common Vulnerabilities and Exposures
(CVE)~\cite{cve} to get an idea of the distribution of
reported \ehi vulnerabilities over time. From the 28 reports we found (Table~\ref*{tab:history}), it can be seen that even though many vulnerabilities were found in earlier years (2005-07), there have been recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.

### 2016-10-25 Discussion/limits.tex
final touches to www paper

\subsection[Limitations]{Limitations}
\label{limitations}
		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions. Measures such as CAPTCHA, hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are often used to detect bots~\cite{captchas3, captchas2}.

@@

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms our system will not be able to find the presence of an \email field. An example is by using the French word for \texttt{e-mail}---courrier {{\'e}}lectronique--- our system is unable to find the presence of the e-mail field.

@@

        E-Mail libraries such as the PHP Extension and Application Repository's (PEAR) mail library provide sanitization for user input. While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries successfully.

        The parser that we use for HTML parsing---Beautiful Soup---does not parse malformed HTML and throws an exception on encountering malformed HTML. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to test web applications with bad HTML markup.

>>>>

\subsection[Limitations]{Limitations}
\label{limitations}
		Because our system is fully automated, it is also susceptible to being stopped by mechanisms in web applications that prevent automated crawls or form submissions. A common reason for our fuzzing attempts to fail is the bot-blocking mechanisms built into the web applications. CAPTCHAs (Completely Automated Public Turing test to tell Computers and Humans Apart)~\cite{captchas2} pose a very difficult problem for our system to exploit \ehi, even if it is present.
		Other measures such as hidden form fields and CSRF (Cross-site Request Forgery~\cite{csrf}) tokens are also often used to detect bots~\cite{captchas3, captchas2}.

@@

        Because we search for the words \texttt{e-mail}, \texttt{mail}, or \texttt{email} within the HTML form, if the website does not use English names for its forms, our system will not be able to find the presence of an \email field. An example is by using the French word for \texttt{e-mail}---courrier {{\'e}}lectronique--- our system is unable to find the presence of the e-mail field.

@@

        E-Mail libraries such as the PHP Extension and Application Repository's (PEAR) mail library provide sanitization for user input. While this is not strictly a limitation of our project, it still means that we are not able to inject sites that used these libraries.

        The parser that we use for HTML parsing---Beautiful Soup---does not parse heavily malformed HTML and throws an exception on encountering such HTML. Thus, we have designed the system to exit gracefully on such occasions. A side-effect of this is that our system is unable to test web applications with very bad HTML markup.

### 2016-10-25 Results/analysis.tex
final touches to www paper

\Emails with the \texttt{bcc} header successfully injected. This form
of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
\ehibcc such \emails in our received \emails. This validates that the
web applications that sent these \emails are vulnerable to \ehi.

\Emails with the \texttt{to} header successfully injected. We
discovered an unintended vulnerability class during our analysis,
which we call \texttt{To~header injection}. These injections reflect
the ability to inject any number of \email addresses into the
\texttt{to} field of the SMTP message while being unable to inject any
other header into the \emails. We found \ehito such \emails in our
received \emails. We attribute this behavior to inconsistent
sanitization by the application.
    % Adam: I can't understand what this sentence is trying to say - Removed.

@@

\Emails with the \texttt{x-check} header successfully injected. The
third category of \emails received were \emails with the
\texttt{x-check} header injected. As discussed in
Section~\ref{analyze:detect_x_check}, we can differentiate between
unsuccessful attempts and successful attempts by injecting the
additional header and checking whether headers other than the
\texttt{bcc} header can be injected into the generated \email.
\ehixcheck \emails were received with the \texttt{x-check} header
injected.

@@

\Email Header Injections with both \texttt{bcc} and \texttt{x-check}
headers. These represent the scenario where an attacker can inject
multiple headers into the \emails. We can see that 54\% of the
received \texttt{bcc} header injected \emails are also susceptible to
being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

Both \texttt{To} header injections and \texttt{x-check} headers. This
combination shows us that in addition to being able to inject into the
\texttt{To} fields, we injected additional headers into the \email. It
is not clear what causes this behavior; however, these can be
exploited to achieve the same result as a regular \ehi.

Total \texttt{x-check} headers and unique \texttt{x-check} headers
found in \texttt{nuser} \emails. We found a total of \ehinuserxcheck
\emails in the \texttt{nuser} account. Out of these,
\ehiuniquenuserxcheck had unique form ids that were \emph{not} already
found in the \texttt{maluser} account. We attribute these \emails to
(probably) being sent by a web application that was built with Python
or another language having a similar behavior with respect to ignoring
duplicate headers while constructing an \email, thus appending the
\texttt{x-check} header and \emph{not} the \texttt{bcc} header.
      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.

Total successful injections. This represents the total number of
successful injections. This includes the \ehi with \texttt{bcc}
header\,(1), \texttt{To} header injections\,(3), and Unique
\texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total
of \success vulnerabilities were found by our system.

>>>>

(1) \Emails with the \texttt{bcc} header successfully injected. This form
of injection was our initial objective, and we found
% Adam: Sai, why isn't this number a command? - DONE.
\ehibcc such \emails in our received \emails. This validates that the
web applications that sent these \emails are vulnerable to \ehi.

(2) \Emails with the \texttt{to} header successfully injected. We
discovered an unintended vulnerability class during our analysis,
which we call \texttt{To~header injection}. These injections reflect
the ability to inject any number of \email addresses into the
\texttt{to} field of the SMTP message while being unable to inject any
other header into the \emails. We found \ehito such \emails in our
received \emails. We attribute this behavior to inconsistent
sanitization by the application.

@@

(3) \Emails with the \texttt{x-check} header successfully injected. The
third category of \emails received were \emails with the
\texttt{x-check} header injected. As discussed in
Section~\ref{analyze:detect_x_check}, we can differentiate between
unsuccessful attempts and successful attempts by injecting the
additional header and checking whether headers other than the
\texttt{bcc} header can be injected into the generated \email.
\ehixcheck \emails were received with the \texttt{x-check} header
injected.

@@

\Email Header Injections with both \texttt{bcc} and \texttt{x-check}
headers: These represent the scenario where an attacker can inject
multiple headers into the \emails. We can see that 54\% of the
received \texttt{bcc} header injected \emails are also susceptible to
being injected with additional headers.
      % Adam: What is the exact percentage? We should use that rather than an approximate number - DONE.

Both \texttt{To} header injections and \texttt{x-check} headers: This
combination shows us that in addition to being able to inject into the
\texttt{To} fields, we injected additional headers into the \email. It
is not clear what causes this behavior; however, these can be
exploited to achieve the same result as a regular \ehi.

Total \texttt{x-check} headers and unique \texttt{x-check} headers
found in \texttt{nuser} \emails: We found a total of \ehinuserxcheck
\emails in the \texttt{nuser} account. Out of these,
\ehiuniquenuserxcheck had unique form ids that were \emph{not} already
found in the \texttt{maluser} account. We attribute these \emails to
(probably) being sent by a web application that was built with Python
or another language having a similar behavior with respect to ignoring
duplicate headers while constructing an \email, thus appending the
\texttt{x-check} header and \emph{not} the \texttt{bcc} header.
      % Adam: What is the actual behavior? This is confusing. - Changed. DONE.

Total successful injections: This represents the total number of
successful injections. This includes the \ehi with \texttt{bcc}
header\,(1), \texttt{To} header injections\,(3), and Unique
\texttt{x-check} headers found in \texttt{nuser} \emails\,(7). A total
of \success vulnerabilities were found by our system.

### 2016-10-25 Results/virus_data.tex
final touches to www paper

\subsection{Emails with Malicious Attachments}
We checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.

To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online virus and malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files. We found that out of the \totalattachmentcount attachments, \totalvirusemails \emails contained malicious attachments, out of which \totalvirusattachmentcount were from unique domains. 
%It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

>>>>

\subsection{Emails with Malicious Attachments}
As additional analysis to find domains on the internet that send out malicious attachments, we checked the \emails received by the `reguser' account (which are injected with regular \email addresses and not malicious data) for the presence of attachments that may contain malicious software, which will indicate that the server itself is not benign.

To do this, we passed the \totalattachmentcount attachments we received to VirusTotal~\cite{virustotal} -- an online malware scanner that checks for the presence of malware by running 40+ virus scanners on the uploaded files. We found that out of the \totalattachmentcount attachments, \totalvirusemails were malicious, out of which \totalvirusattachmentcount were from unique domains. This data is just a by-product of our research and could very well lead to future research.
%It is to be noted that none of these domains were found on the spam analysis we did earlier, indicating that if these could be exploited, we could send emails with malicious attachments to other people using these servers.

### 2016-10-25 System/components.tex
final touches to www paper

%TODO Adam: made clear that ALL input fields that appear in the email are fuzzed, with examples like name, username, etc.
To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email. These could be fields such as name, date of birth, username, etc. If they do, we add them to the list of fields that can \emph{potentially} result in an \ehi vulnerability for the given \email.

>>>>

%TODO Adam: made clear that ALL input fields that appear in the email are fuzzed, with examples like name, username, etc.
To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear in either the headers or body of the \email. These could be fields such as name, username, age, etc. If they do, we add them to the list of fields that can \emph{potentially} result in an \ehi vulnerability for the given \email.

### 2016-10-25 rel_work.tex
final touches to www paper

% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
There are different approaches to finding vulnerabilities in web applications, and most approaches will be either Black-Box testing or White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699, Huang, kals2006secubat, payet13:ears-in-the-wild, zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012, Doupe2010}.

@@

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. Terada also describes proof-of-concept attacks against certain mailing libraries such as \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper makes this observation and discusses why it is different from \ehi.

@@

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes the vulnerability. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability. Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).

>>>>

% Adam: Sai, can you combine all the \cites at the same line like I did for the others? 
There are different approaches to finding vulnerabilities in web applications, and most approaches use either Black-Box testing or White-Box testing.
Our work is based on the black-box testing approach to finding vulnerabilities on websites, and research has made use of this methodology to find vulnerabilities in web applications~\cite{Beizer:1995:BTT:202699, Huang, kals2006secubat, payet13:ears-in-the-wild, zanero2005automatic}. There has been significant discussion on both the benefits of such an approach~\cite{black-box} and its shortcomings~\cite{Doupe2012, Doupe2010}.

@@

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. Terada also describes proof-of-concept attacks against certain mailing libraries such as \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. Terada's paper also makes this observation and discusses why it is different from \ehi.

@@

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes the vulnerability. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability. Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.
\ehi vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).
